---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Rocco Incardona



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE

cces_filtered <- cces %>% mutate(ideo5 = recode(ideo5,`1`="Very Liberal",`2`="Liberal",
                                                `3`="Moderate",`4`="Conservative",`5`="Very Conservative"))


ggplot(data = cces_filtered, aes(x = ideo5, fill=ideo5))+  geom_bar()+
  labs(y="Count", x="Ideology")+
  ggtitle("Respondent Ideology")+
  guides(fill="none")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE

cces_filtered2 <- cces_filtered %>% mutate(pew_religimp = recode(pew_religimp,`1`="Very imp.",`2`="Somewhat imp.",
                                                `3`="Not too imp.",`4`="Not imp.")) %>% rename(Ideology = ideo5)


ggplot(data = cces_filtered2, aes(x = pew_religimp, fill=Ideology))+  geom_bar()+
  labs(y="Count", x="Importance of Religion")+
  ggtitle("Importance of Religion by Ideology")

```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE

semester <- rep(seq(from=1,to=6,by=1), 3)
grade <- runif(18,min = 80, max = 100)
student <- c(rep("Amanda", 6), rep("Betty", 6),rep("Carol", 6))
fig_data <-tibble("Semester"=semester,"Student"=student, "Grade"=grade)


ggplot(fig_data,(aes(x=Semester,y=Grade, group = Student, color = Student)))+ 
  geom_line() +
  facet_wrap(~Student) +
  labs(y="Grade", x="Semester")+
  ggtitle("Student Grades by Semester")+
  theme(legend.position = "none")
```
