---
title: "Data Review"
author: "Rocco Incardona"
date: "25/04/2022"
output: html_document
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.


#https://econandrew.github.io/wdi-api-R-gettingstarted/using-r-to-access-the-world-bank-api.html
#install.packages("wbstats")

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(wbstats)

```

## Import Your Data

In the following code hunk, import your data.

```{r data_import}

#### Use read_csv() or another function
# Environment:
  # EN.BIR.THRD.NO Environment: Biodiversity & protected areas Bird species, threatened
  # EN.FSH.THRD.NO Environment: Biodiversity & protected areas Fish species, threatened
  # EN.HPT.THRD.NO Environment: Biodiversity & protected areas Plant species (higher), threatened
  # EN.MAM.THRD.NO Environment: Biodiversity & protected areas Mammal species, threatened
  # EN.POP.DNST Environment: Density & urbanization Population density (people per sq. km of land area)
  # SP.URB.TOTL.IN.ZS Environment: Density & urbanization Urban population (% of total population)
  # EN.ATM.CO2E.KT Environment: Emissions Total CO2 emissions (thousand metric tons of CO2 excluding Land-Use Change and Forestry)
  # EN.ATM.GHGT.KT.CE Environment: Emissions Total greenhouse gas emissions (thousand metric tons of CO2 equivalent excluding Land-Use Change and Forestry)
  # EG.ELC.FOSL.ZS Environment: Energy production & use Electricity production from oil, gas and coal sources (% of total)
# EG.USE.COMM.CL.ZS Environment: Energy production & use Alternative and nuclear energy (% of total energy use)
# EG.IMP.CONS.ZS Environment: Energy production & use Energy imports, net (% of energy use)
# Economy:
# NY.GDP.MKTP.PP.CD Economic Policy & Debt: Purchasing power parity GDP, PPP (current international $)
# NY.GDP.PCAP.PP.CD Economic Policy & Debt: Purchasing power parity GDP per capita, PPP (current international $)
# NE.RSB.GNFS.ZS Economic Policy & Debt: National accounts: Shares of GDP & other External balance on goods and services (% of GDP)
# NE.TRD.GNFS.ZS Economic Policy & Debt: National accounts: Shares of GDP & other Trade (% of GDP)
# NV.IND.MANF.ZS Economic Policy & Debt: National accounts: Shares of GDP & other Manufacturing, value added (% of GDP)
# NE.CON.PRVT.PP.CD Economic Policy & Debt: Purchasing power parity Households and NPISHs Final consumption expenditure, PPP (current international $)
# Society:
# SP.POP.TOTL Health: Population: Structure Population, total
# SP.POP.GROW Health: Population: Dynamics Population growth (annual %)
# SP.DYN.TFRT.IN Health: Reproductive health Fertility rate, total (births per woman)
# HD.HCI.OVRL Public Sector: Policy & institutions Human capital index (HCI) (scale 0-1)
# IQ.CPA.GNDR.XQ Public Sector: Policy & institutions CPIA gender equality rating (1=low to 6=high)
# SP.DYN.CBRT.IN Health: Population: Dynamics Birth rate, crude (per 1,000 people)
# SP.DYN.CDRT.IN Health: Population: Dynamics Death rate, crude (per 1,000 people)
# VC.IDP.NWCV Public Sector: Conflict & fragility Internally displaced persons, new displacement associated with conflict and violence (number of cases)
# VC.IDP.NWDS Public Sector: Conflict & fragility Internally displaced persons, new displacement associated with disasters (number of cases)
# VC.IDP.TOCV Public Sector: Conflict & fragility Internally displaced persons, total displaced by conflict and violence (number of people)
#### Make sure your data is converted into a tibble. 

list_indicators <- c("EN.BIR.THRD.NO", "EN.FSH.THRD.NO", "EN.POP.DNST")

society <- c("EN.POP.DNST")


df <- wb_data(country = "countries_only", indicator = society)
df

plot(df$EN.POP.DNST)

max(df$EN.POP.DNST, na.rm = TRUE)

    ```

## Part 1

Using words, describe the visualization you are going to make using which variables/characteristics in your data:

*Example*: For my first figure, I am going to create a scatterplot that plots vehicle weight on the x axis and miles per gallon the y axis. I will create a two column tibble with these data.

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_1}
fig_dat1<-dat %>% select(wt,mpg)
####make sure you call the data so it will display in your report
fig_dat1
```

## Part 2

Using words, describe the *second* visualization you are going to make using which variables/characteristics in your data:

*Example*: For my second figure, I am going to create a boxplot that includes three boxplots for miles per gallon, horsepower, and weight.

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_2}
fig_dat2<-dat %>% select(mpg,hp,wt)
####make sure you call the data so it will display in your report
fig_dat2
```


## Part 3

Using words, describe the *third* visualization you are going to make using which variables/characteristics in your data:

*Example*: For the third figure, I will display a density plot of the quarter mile time for six cylinder cars.

```{r data_3}
fig_dat3<-dat %>% filter(cyl==6) %>% select(qsec) 
####make sure you call the data so it will display in your report
fig_dat3
```

