---
title: "Data Review"
author: "Rocco Incardona"
date: "25/04/2022"
output: html_document
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.


#https://cran.r-project.org/web/packages/wbstats/vignettes/wbstats.html
#install.packages("wbstats")
#install.packages("tictoc")

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(wbstats)
library(tictoc)
library(plotly)

```

## Data import and availability

In the following code chunk, I import my data and visualize how many countries are available over time for each indicator.

```{r data_import, , warning=FALSE}

environment <- c("EN.POP.DNST", "EN.ATM.CO2E.KT", "EN.ATM.GHGT.KT.CE", "EG.ELC.FOSL.ZS")
economy <- c("NY.GDP.MKTP.PP.CD", "NY.GDP.PCAP.PP.CD", "NE.RSB.GNFS.ZS")
society <- c("SP.POP.TOTL", "SP.POP.GROW")
all_indicators <- c(environment,economy,society)

tic()
df <- wb_data(country = "countries_only", indicator = all_indicators, start_date = 1980, end_date = 2022)
toc()
dim(df)

# Check available data
#df %>% group_by(date) %>% summarise_all(funs(sum(!is.na(.)))) %>% print(n = Inf)

df %>% group_by(date) %>% summarise_all(funs(sum(!is.na(.)))) %>%
  gather(key="measure", value="value", all_indicators) %>%
  ggplot(aes(x = date, y = value)) + geom_bar(stat = "identity") +
  facet_wrap(~measure)

summary(df)

# indicator <- "EG.ELC.FOSL.ZS"
# df %>% select(country, date, indicator) %>% filter(!is.na(indicator)) %>% select(country) %>% unique %>% print(n = Inf)
#wb_search("SP.POP.TOTL")

```

## Part 1

For my first figure, I am going to create an interactive choropleth displaying for most of the countries of the world one of the following indicators from 1980 to 2022:

* EN.ATM.CO2E.KT Environment: Emissions Total CO2 emissions (thousand metric tons of CO2 excluding Land-Use Change and Forestry);
* SP.POP.TOTL Health: Population: Structure Population, total);
* NY.GDP.MKTP.PP.CD Economic Policy & Debt: Purchasing power parity GDP, PPP (current international $)

The data will be extracted from the World Bank using the wbstats package and will be structured as a tibble containing 5 columns (the three indicators plus the country and the date). Data will be visualized with plotly.

```{r data_1}
fig_dat1<-df %>% select(iso3c, country,date, EN.ATM.CO2E.KT, SP.POP.TOTL, NY.GDP.MKTP.PP.CD) %>% filter(date>=1980)

####make sure you call the data so it will display in your report
fig_dat1

# plot_ly(fig_dat1, type='choropleth', locations=fig_dat1$iso3c, z=fig_dat1$SP.POP.TOTL, text=fig_dat1$country, colorscale="Blues")

```

## Part 2

For my second figure, I am going to create a dynamic bar chart, which displays the top 10 countries which have emitted the most CO2 each year from 1980 to 2020 (e.g. example here https://towardsdatascience.com/create-animated-bar-charts-using-r-31d09e5841da).
Example of extraction for one year below:

```{r data_2}
fig_dat2<-df %>% select(iso3c, country,date, EN.ATM.CO2E.KT) %>% filter(date==2000) %>% slice_max(EN.ATM.CO2E.KT, n = 10)
  
####make sure you call the data so it will display in your report
fig_dat2
```


## Part 3

For the third figures, I will display a scatter plot showing the interaction between the following environmental and economic variables:

* NY.GDP.PCAP.PP.CD Economic Policy & Debt: Purchasing power parity GDP per capita, PPP (current international $)
* Total greenhouse gas emissions per capita, obtained as a ratio of the following variables:

    + EN.ATM.GHGT.KT.CE Environment: Emissions Total greenhouse gas emissions (thousand metric tons of CO2 equivalent excluding Land-Use Change and Forestry)
    + SP.POP.TOTL Health: Population: Structure Population, total);

The scatter plot will be animated to show the evolution over time.

Example of extraction for one year below:

```{r data_3}

fig_dat3<-df %>% select(iso3c, country,date, SP.POP.TOTL, NY.GDP.PCAP.PP.CD, EN.ATM.GHGT.KT.CE) %>%
mutate(green_house_emissions_pc = EN.ATM.GHGT.KT.CE/SP.POP.TOTL) %>% filter(date==2015)
  
####make sure you call the data so it will display in your report
fig_dat3

#ggplot(fig_dat3, aes(x=NY.GDP.PCAP.PP.CD, y=green_house_emissions_pc)) + geom_point() +  geom_text(aes(label = iso3c))

```



