---
title: "Visualization Critique"
author: "Rocco Incardona"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualization Link

Please provide a link to your visualization critique.

I have decided to analyse the following chart extracted from r/DataIsBeautiful:
https://www.reddit.com/r/dataisbeautiful/comments/tylkr8/oc_there_is_a_world_shortage_of_wheat_russia_is/

```{r out.width="300px"}
url <- "https://i.redd.it/dg93eqsav5s81.png"
knitr::include_graphics(url)

```


## Weakness

What do you see as a significant weakness of this visualization? How could you improve it to make it clearer, easier to understand, or more impactful? Make sure you provide some detail in justifying your answer.

Despite the great impact of its graphics, I believe it is worth to mention the following weaknesses:

* Figures on the map are not easily comparable (see the big gap between Turkey and Kazakhstan)
* the amount of data displayed is very limited (only five figures) and does not include for instance any information on the other importers
* The color also does not seem to be used to denote any change in value: Russia appears in bright yellow while importers have all the same color.
* Given that Ukraine is also a large producer of wheat I would have tried to include this information as comparison

To better have an idea of the proportions, the map could be paired with a bar charts. A bar chart could also include more countries. Finally, I would have included a reference to the overall export of wheat from Russia.

## Strength

What do you see as a strength of this visualization? Is there a specific choice of the designer that made it especially useful or impactful? Make sure you provide some detail in justifying your answer.

Among the strengths of this visualization:

* Simplicity - The amount of data is limited and therefore easy to absorbe, while the nice visual and color are catchy and connected to the topic (arrows = flows, yellow + symbols = wheat)
* Infographic format, therefore easy to share on social networks
* The title and the source are clearly specified, so the reader can try to find more information on the topic
* Non relevant areas are greyed out.

Clearly the author wanted to design something that is simple and eye-catchy and that can be shared quickly.
This was done at the cost of the amount of information displayed




