---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Requirements
Using ggplot, create a scatter plot, a distribution figure (box plot, histogram, or density plot), bar plot, and line plot.
Use colors and facetting in at least one of your figures.
Add a text annotation to at least one of the your figures.
Use a ggtheme for one of your figures.
Make sure your figures have titles and appropriately labeled axes.

### Put your name here: Rocco Incardona

## Exercise 1

Explain what you are visualizing here: 
Ideology vs percentage of votes won in the 115th LES.Democratic members of the congress are less
conservative and they also managed to win elections with larger shares of votes.
Manual colors are set for this figure.

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE

cel %>% filter(congress == 115) %>% mutate(Party = recode(dem,`1`="Democrat",`0`="Republican")) %>%

ggplot(aes(x = meddist, y = votepct, color = Party))+geom_point()+
  labs(x = "Distance from median ideology", y="% of votes won in the election") +  
  scale_colour_manual(values = c("red", "blue")) +
  ggtitle("Ideology vs percentage of votes won in the 115th LES")


```

## Exercise 2

Explain what you are visualizing here: 
Family income by region and gender split. Female tend to have lower family income, especially in Northwest and West regions.
Manual colors and facetting used in this chart.

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE


cces %>% mutate(Gender = recode(gender,`1`="Male",`2`="Female")) %>%
  mutate(Region = recode(region,`1`="Northwest",`2`="Midwest",`3`="South",`4`="West")) %>% 
  mutate(Region = recode(educ,`1`="Northwest",`2`="Midwest",`3`="South",`4`="West",`5`="South",`6`="West")) %>% 

  ggplot(aes(y = faminc_new, x = Gender, color = Gender)) + geom_boxplot() +#geom_histogram(binwidth = 0.5) + 
  facet_grid(cols = vars(Region)) +
  labs(y="Family income") +
  scale_colour_manual(values = c("red", "blue")) +
  ggtitle("Family income by region and gender") +
  theme(legend.position = "none")

  
```

## Exercise 3

Explain what you are visualizing here:
Religion importance by origin of the respondent. Respondents with hispanic origin tend to
give higher importance to religion. 
ggtheme, manual colors and text annotations are used in this chart.
Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE
library("ggthemes")

percentData <- cces %>% mutate(pew_religimp = recode(pew_religimp,`1`="Very important",`2`="Somewhat important", `3`="Not too important ",`4`="Not at all important"))  %>%
        mutate(hispanic = recode(hispanic,`1`="Hispanic",`2`="Not hispanic")) %>% group_by(hispanic) %>%          count(pew_religimp) %>%
        mutate(ratio=scales::percent(n/sum(n)))
percentData

cces %>% mutate(pew_religimp = recode(pew_religimp,`1`="Very important",`2`="Somewhat important",
                                  `3`="Not too important ",`4`="Not at all important"))  %>%
        mutate(hispanic = recode(hispanic,`1`="Hispanic",`2`="Not hispanic"))  %>%


ggplot(aes(x = factor(hispanic), fill=factor(pew_religimp)))+  
  geom_bar(position="fill")+
  labs(y="Share of respondents", x="Origin of the respondent")+
  ggtitle("Religion importance by origin of the respondents") +
  theme_economist() + scale_colour_economist() +
  theme(legend.text=element_text(size=9),legend.title=element_blank(),
        axis.text.y=element_blank()) +
  scale_fill_brewer(direction = 1, palette = "Blues") +
    geom_text(data=percentData, aes(y=n,label=ratio),
              position=position_fill(vjust=0.5))




```

## Exercise 4

Explain what you are visualizing here: 
Revenues of three companies over time for one year.
ggtheme and manual colors are used in this chart.

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE
library(scales)
month <- rep(seq(from=1,to=12,by=1), 3)

mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")

revenues <- runif(36,min = 60000, max = 100000)
company <- c(rep("Company1", 12), rep("Company2", 12),rep("Company3", 12))
fig_data <-tibble("Month"=mymonths[month],"Company"=company, "Revenues"=revenues)

ggplot(fig_data,(aes(x=reorder(Month,month),y=Revenues, group = Company, color = Company)))+ 
  geom_line() +
  facet_wrap(~Company) +
  labs(y="Revenues", x="Month")+
  ggtitle("Company revenues in 2019")+
  theme_wsj()+ scale_colour_wsj() +
  scale_y_continuous(labels = unit_format(unit = "K", scale = 1e-3))+
  theme(legend.position = "none",plot.title = element_text(size = 28, face = "bold"),
        axis.text.x = element_text(angle = 90, size = 10))


```
