---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Requirements
Using ggplot, create a scatter plot, a distribution figure (box plot, histogram, or density plot), bar plot, and line plot.
Use colors and facetting in at least one of your figures.
Add a text annotation to at least one of the your figures.
Use a ggtheme for one of your figures.
Make sure your figures have titles and appropriately labeled axes.

### Put your name here: Rocco Incardona

## Exercise 1

Explain what you are visualizing here: 
Ideology vs percentage of votes won in the 115th LES.Democratic members of the congress are less
conservative and they also managed to win elections with larger shares of votes.
Manual colors are set for this figure.

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE

cel_filtered <- cel %>% filter(congress == 115) %>% mutate(Party = recode(dem,`1`="Democrat",`0`="Republican"))

ggplot(data = cel_filtered, aes(x = meddist, y = votepct, color = Party))+geom_point()+
  labs(x = "Distance from median ideology", y="% of votes won in the election") +  
  scale_colour_manual(values = c("red", "blue")) +
  ggtitle("Ideology vs percentage of votes won in the 115th LES")


```

## Exercise 2

Explain what you are visualizing here: Distribution figure - histogram 

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE

ces


ggplot(data = cel_filtered2, aes(x = votepct, y = all_pass, color = Gender))+geom_point()+
  labs(x = "Vote Percentage", y="Bills Passed")+facet_grid(cols = vars(majority))+
  scale_colour_manual(values = c("orange", "green"))

cces %>% mutate(Gender = recode(gender,`1`="Male",`2`="Female")) %>%
  mutate(Region = recode(region,`1`="Northwest",`2`="Midwest",`3`="South",`4`="West")) %>% 
  mutate(Region = recode(educ,`1`="Northwest",`2`="Midwest",`3`="South",`4`="West",`5`="South",`6`="West")) %>% 
  
  
  
  ggplot(aes(faminc_new, fill = Gender)) + geom_histogram(binwidth = 0.5) + 
  facet_grid(cols = vars(Region))


  
```

## Exercise 3

Explain what you are visualizing here: Bar plot

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE

cces_filtered <- cces %>% mutate(ideo5 = recode(ideo5,`1`="Very Liberal",`2`="Liberal",
                                                `3`="Moderate",`4`="Conservative",`5`="Very Conservative"))


ggplot(data = cces_filtered, aes(x = ideo5, fill=ideo5))+  geom_bar()+
  labs(y="Count", x="Ideology")+
  ggtitle("Respondent Ideology")+
  guides(fill="none")


```

## Exercise 4

Explain what you are visualizing here: Line plot

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

semester <- rep(seq(from=1,to=6,by=1), 3)
grade <- runif(18,min = 80, max = 100)
student <- c(rep("Amanda", 6), rep("Betty", 6),rep("Carol", 6))
fig_data <-tibble("Semester"=semester,"Student"=student, "Grade"=grade)


ggplot(fig_data,(aes(x=Semester,y=Grade, group = Student, color = Student)))+ 
  geom_line() +
  facet_wrap(~Student) +
  labs(y="Grade", x="Semester")+
  ggtitle("Student Grades by Semester")+
  theme(legend.position = "none")

```
