---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Requirements
Using ggplot, create a scatter plot, a distribution figure (box plot, histogram, or density plot), bar plot, and line plot.
Use colors and facetting in at least one of your figures.
Add a text annotation to at least one of the your figures.
Use a ggtheme for one of your figures.
Make sure your figures have titles and appropriately labeled axes.

### Put your name here: Rocco Incardona

## Exercise 1

Explain what you are visualizing here: Scatter plot

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE


cel_filtered <- cel %>% filter(congress == 115) %>% mutate(Gender = recode(female,`1`="Female",`0`="Male"))

ggplot(data = cel_filtered, aes(x = dwnom1, y = all_pass, color = Gender))+geom_point()+labs(x = "Ideology", y="Bills Passed")

```

## Exercise 2

Explain what you are visualizing here: Distribution figure - histogram 

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE

c + geom_histogram(binwidth = 5)
x, y, alpha, color, fill, linetype, size, weight
  
```

## Exercise 3

Explain what you are visualizing here: Bar plot

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE

cces_filtered <- cces %>% mutate(ideo5 = recode(ideo5,`1`="Very Liberal",`2`="Liberal",
                                                `3`="Moderate",`4`="Conservative",`5`="Very Conservative"))


ggplot(data = cces_filtered, aes(x = ideo5, fill=ideo5))+  geom_bar()+
  labs(y="Count", x="Ideology")+
  ggtitle("Respondent Ideology")+
  guides(fill="none")


```

## Exercise 4

Explain what you are visualizing here: Line plot

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

semester <- rep(seq(from=1,to=6,by=1), 3)
grade <- runif(18,min = 80, max = 100)
student <- c(rep("Amanda", 6), rep("Betty", 6),rep("Carol", 6))
fig_data <-tibble("Semester"=semester,"Student"=student, "Grade"=grade)


ggplot(fig_data,(aes(x=Semester,y=Grade, group = Student, color = Student)))+ 
  geom_line() +
  facet_wrap(~Student) +
  labs(y="Grade", x="Semester")+
  ggtitle("Student Grades by Semester")+
  theme(legend.position = "none")

```
